An investigation of the clinical utility of preoperative cardiopulmonary exercise testing in patients undergoing major pancreatic surgery.

### 2016-02-14 Presentations/viva_presentation_short.tex
Viva Presentation - Donny comments
- Next add transitions

\documentclass[10pt]{beamer}

@@

\begin{frame}
	\frametitle{My Supervisors - Thank you!}
	I wish to thank the following people for their unwavering support through the past few years. I thank them especially for their faith that I will see this through and if they had any doubts, for not telling me about them.\\
	\bigskip
	Professor Donald C McMillan,\\
	University Department of Surgery, Glasgow Royal Infirmary\\
	\bigskip
	Professor Paul Horgan,\\
	University Department of Surgery, Glasgow Royal Infirmary\\
\end{frame}

@@

\begin{frame}
	\frametitle{Pancreatic cancer} %Epidemiology/outcomes
	\begin{block}{The Problem}
		\begin{itemize}
			\item 10th common but 5th common cause of cancer death
			\item Survival	1-yr: 20.8\%, 5-yr: 3.3\%, 10yr: 1.1\%
			\item Operable disease : approx 15\%
		\end{itemize}
	\end{block}
	\begin{block}{Treatment}
		\begin{itemize}
			\item Surgery + adjuvant chemotherapy only chance of cure
		\end{itemize}
	\end{block}
	\begin{block}{Pancreaticoduodenectomy}
		\begin{itemize}
			\item Complex surgery with 50\% morbidity
			\item Performed only in specialist centres
			\item Patient fitness is as important as tumour factors
			\item Adjuvant treatment improves survival
		\end{itemize}
	\end{block}
\end{frame}

\begin{frame}
	\frametitle{Pancreaticoduodenectomy}
	\framesubtitle{Postoperative complications}
	\begin{itemize}
		\item Significant improvements in mortality ($<$5\% from $>$40\%)
		\item Morbidity remains high at over 40\%
		\item Postoperative pancreatic fistula (POPF) is serious
		\item POPF can lead to other complications: Sepsis, PPH, DGE
		\item International Study Group for Pancreatic Surgery
		\item Clavien-Dindo classification of complications
	\end{itemize}
\end{frame}

@@

\begin{frame}
	\frametitle{Receiver operating characteristics analysis}
	\framesubtitle{CRP thresholds for predicting infective complications in the absence of a POPF. }
	\begin{columns}
		\column[c]{0.45\textwidth}
			\begin{figure}
				\includegraphics[width=\textwidth]{../Figures/crp_comp_ROC_infection_D3}
				\\{\scriptsize D3 178 mg/dl; AUC 0.64; NPV 0.79; \\Spec 0.66; Sens 0.64; p=0.011}
			\end{figure}
		\column[c]{0.45\textwidth}
			\begin{figure}
				\includegraphics[width=\textwidth]{../Figures/crp_comp_ROC_infection_D4}
				\\{\scriptsize D4 125 mg/dl; AUC 0.71; NPV 0.83; \\Spec 0.64; Sens 0.74; p$<$0.001}
			\end{figure}
	\end{columns}
\end{frame}

\section[Chapter 7]{Discussion}

% Discuss the results in the context of a patient.
% 63 yr old female with BMI of 35 presents with painless OJ
% PMH - HTN, T2DM, smoked 10/day for 40 yrs
% Bloods: Bil 180, CRP 22, Alb 30
% Investigations reveal an operable tumour of the head of the pancreas
% How would this patient have been managed 10 years ago?
\section{Case study}
\begin{frame}
	\frametitle{A case study}
	\framesubtitle{How does this work influence decision-making?}
	\begin{itemize}
		\item 63 yr old female with BMI of 35 presents with painless OJ
		\item PMH - HTN, T2DM, smoked 10/day for 40 yrs
		\item Bloods: Bil 180, CRP 22, Alb 30
		\item Imaging: Resectable tumour of head of pancreas
		\medskip
		\item Should this patient undergo CPET?
		\item Should this patient undergo biliary drainage?
		\item Should we wait until resolution of jaundice before CPET?
		\item How can the CPET results be used to influence her care?
		\item How can the postoperative inflammatory markers be used to manage her care?
	\end{itemize}
\end{frame}

@@

\begin{frame}
	\frametitle{Future directions}
	\begin{itemize}
		\item Assessing impact of prehabilitation
		\item Assessing impact of neo-adjuvant treatments
		\item Does CPET predict long-term survival?
		\item Improvements in aerobic capacity and body composition through nutritional supplementation and physical exercise
		\item Correction of anaemia through preoperative iron supplementation
		\item Early recognition and aggressive management of complications
		\item Assessing suitability for 'fast-track' to surgery and 'enhanced-recovery'
	\end{itemize}

\section{The End}

\begin{frame}
\frametitle{The End}
\framesubtitle{Tools and Roles}

>>>>

\documentclass[10pt]{beamer}
%\documentclass[handout, 10pt]{beamer}
\setbeamercovered{transparent}

@@

%\begin{frame}
%	\frametitle{My Supervisors - Thank you!}
%	I wish to thank the following people for their unwavering support through the past few years. I thank them especially for their faith that I will see this through and if they had any doubts, for not telling me about them.\\
%	\bigskip
%	Professor Donald C McMillan,\\
%	University Department of Surgery, Glasgow Royal Infirmary\\
%	\bigskip
%	Professor Paul Horgan,\\
%	University Department of Surgery, Glasgow Royal Infirmary\\
%\end{frame}

@@

\begin{frame}
	\frametitle{Pancreatic cancer} %Epidemiology/outcomes
	\begin{block}{The Problem}
		\begin{itemize}
			\item 10th common but 5th common cause of cancer death
			\item Survival	1-yr: 20.8\%, 5-yr: 3.3\%, 10yr: 1.1\%
			\item Operable disease : approx 15\%
		\end{itemize}
	\end{block}
	\begin{block}{Treatment}
		\begin{itemize}
			\item Surgery + adjuvant chemotherapy only chance of cure
		\end{itemize}
	\end{block}
	\begin{block}{Pancreaticoduodenectomy}
		\begin{itemize}
			\item Complex surgery with 40\% morbidity
			\item Performed only in specialist centres
			\item Patient fitness is as important as tumour factors
			\item Adjuvant treatment improves survival
		\end{itemize}
	\end{block}
\end{frame}

\begin{frame}
	\frametitle{Pancreaticoduodenectomy}
	\framesubtitle{Postoperative complications}
	\begin{itemize}
		\item Significant improvements in mortality ($<$5\% from $>$40\%)
		\item Morbidity remains high at over 40\%
		\item Postoperative pancreatic fistula (POPF) is serious
		\item POPF can lead to other complications: Sepsis, PPH, DGE
		\item International Study Group for Pancreatic Surgery
		\item Clavien-Dindo classification of complications
		\medskip
		\item Complications may preclude adjuvant treatment
		\item Median survival is approximately 18 months
		\item Adjuvant treatment improves this by 2-3 months
	\end{itemize}
\end{frame}

@@

\begin{frame}
	\frametitle{Receiver operating characteristics analysis}
	\framesubtitle{CRP thresholds for predicting infective complications in the absence of a POPF. }
	\begin{columns}
		\column[c]{0.45\textwidth}
			\begin{figure}
				\includegraphics[width=\textwidth]{../Figures/crp_comp_ROC_infection_D3}
				\\{\scriptsize D3 178 mg/dl; AUC 0.64; NPV 0.79; \\Spec 0.66; Sens 0.64; p=0.011}
			\end{figure}

		\column[c]{0.45\textwidth}
			\begin{figure}
				\includegraphics[width=\textwidth]{../Figures/crp_comp_ROC_infection_D4}
				\\{\scriptsize D4 125 mg/dl; AUC 0.71; NPV 0.83; \\Spec 0.64; Sens 0.74; p$<$0.001}
			\end{figure}
	\end{columns}
\end{frame}

\section[Chapter 7]{Discussion}
\begin{frame}
	\frametitle{Future directions}
	\begin{itemize}
		\item Assessing impact of prehabilitation
		\item Improving in aerobic capacity and body composition through nutritional supplementation and physical exercise
		\item Assessing impact of neo-adjuvant treatments
		\item Customising goal-directed therapy based on CPET
		\item Correction of anaemia through preoperative iron supplementation
		\item Early recognition and aggressive management of complications
		\item Assessing suitability for 'fast-track' to surgery and 'enhanced-recovery'
	\end{itemize}
\end{frame}

\section{Case study}
\begin{frame}
	\frametitle{A case study}
	\framesubtitle{How does this work influence decision-making?}
	\begin{itemize}
		\item 63 yr old female with BMI of 35 presents with painless OJ
		\item PMH - HTN, T2DM, ex-smoker
		\item Bloods: Bil 180, CRP 22, Alb 30
		\item Imaging: Resectable tumour of head of pancreas
		\medskip

		\item Should this patient undergo CPET?
		\item Should this patient undergo biliary drainage?
		\item Should we wait until resolution of jaundice before CPET?
		\item How can the CPET results be used to influence her care?
		\item How can the postoperative inflammatory markers be used to manage her care?
	\end{itemize}
\end{frame}

@@

\begin{frame}
\centerline{Thank You}
\end{frame}

\begin{frame}
\frametitle{Tools and Roles}
%\framesubtitle{Tools and Roles}
